ICT and Future Productivity:\\Evidence and Theory of a GPT\thanks{Correspondence: Department of Economics, Boston College, 140 Commonwealth Avenue, Chestnut Hill, MA 02467. Email: brianti@bc.edu (Marco Brianti) and gati@bc.edu (Laura G\'ati).}

### 2018-07-01 Latex/Draft_Summer2018/Summer2018.tex
read up to the empirical part that you have written
I think this paper will be great! I’m very enthusiastic! :)

In addition, Table \ref{table:vardec} in Appendix \ref{section:vardec} presents forecast error variance decompositions for the ICT shock on each variable. The table shows decompositions on impact, and at a one-, two-, four-, six-, and ten-year horizon. In line with the impulse responses, ICT shocks, which are orthogonal to current productivity, explain nothing of current TFP fluctuations. At a ten-year horizon, however, this fraction is over a third! On the other hand, ICT shocks drive almost the whole variation in ICT investment on impact but this effect tends to decay over time getting below the $50$\% after 10 years. Interestingly, both output and consumption has a remarkable reaction on impact: $26$\% and $19$\%, respectively. Moreover, this effect tends to increase reaching $40$\% in both cases over the maximal horizon. Finally, ICT shocks do not have a remarkable effect on relative prices. The fraction of fluctuations explained on impact is only $6$\% with a peak of $14$\% between four and six years.

@@

In this section, we show a set of robustness checks aimed to show that our previous results are not driven by future signals regarding exogenous productivity. Although our results are robust when we purposely change the main specification presented in Subsection \ref{section:mainSpec}, an important critique to our empirical strategy is reverse causality coming from news on future TFP. As suggested by the news-shock literature, the positive reaction of ICTI on impact may be triggered by signals related future increases in productivity and not to a contemporaneous ICT shock. In other words, our identification strategy may confound our shock of interest with a news shock which contemporaneously enhances investment in ICT capital goods. We address this issue by providing two main alternative identification strategies which we show deliver the same time series of ICT shocks as our initial specification. Firstly, we test if our result is robust once removed all the forward looking variables which fluctuations may be unrelated to sector-specific technological changes: consumption and output. Technically speaking, consumption and output may granger-cause future TFP for reasons which are orthogonal to ICT shocks. For example, the forward-looking nature of consumption may provide to the VAR unnecessary information regarding future changes in TFP not related to an ICT shock which our identification strategy is not able to filter it out. Secondly, we apply a sequential identification where we firstly identify a news shock in the spirit of \cite{barsky2011news}, and subsequently we identify our sectoral ICT shock using the previous identification strategy. This second strategy has the specific purpose of filtering out all the current movements in forward-looking variables related to future fluctuations of TFP which are not related to current ICT shocks.

Encouragingly, controlling for signals regarding future movements in productivity does not affect our identified ICT shocks suggesting a causal relation which goes from current ICT investment to future TFP.

>>>>

In addition, Table \ref{table:vardec} in Appendix \ref{section:vardec} presents forecast error variance decompositions for the ICT shock on each variable. The table shows decompositions on impact, and at a one-, two-, four-, six-, and ten-year horizon. These results are very interesting in their own right, as they hint that the ICT sector may have a particular role for the overall productivity of the economy.

In line with the impulse responses, ICT shocks, which are orthogonal to current productivity, explain nothing of current TFP fluctuations. At a ten-year horizon, however, this fraction is over a third! This crucial result is a strong sign that the ICT sector matters for overall productivity over and beyond the direct contribution of its sectoral productivity (which, as we have seen, is marginal). At the same time, ICT shocks drive almost the whole variation in ICT investment on impact, with a slow decay over time to below $50$\% after 10 years. Interestingly, both output and consumption have a remarkable reaction on impact: $26$\% and $19$\%, respectively. Moreover, this effect tends to increase reaching $40$\% in both cases at the maximal horizon. Finally, ICT shocks only account for a small fraction of movements in relative prices. The fraction of fluctuations explained on impact is only $6$\% with a peak of $14$\% between four and six years. Overall, these variance decompositions all seem to suggest that the ICT shock leads to complex forms of reallocation and accumulation that take place over the medium run in the economy. Our structural model of Section \ref{section:theory} provides a theoretical framework to think about these dynamics and to give them an economic interpretation.

@@

In this section, we present a set of robustness checks aimed to show that our previous results are not driven by future signals regarding exogenous productivity. The main concern against the specification of \ref{section:mainSpec} is reverse causality coming from the presence of news about future TFP that is not accounted for. Indeed, the news-shock literature warns that the positive reaction of ICTI on impact may be triggered by signals related to future increases in productivity and not to a contemporaneous ICT shock. In other words, our identification strategy may confound our shock of interest with a news shock which contemporaneously enhances investment in ICT capital goods. We address this issue by providing two main alternative identification strategies which we show deliver the same time series of ICT shocks as our initial specification.

As a first-pass test, % cite Barsky Basu Lee and Forni or whatevs
we check if our results are robust once we remove all the forward looking variables whose fluctuations may be unrelated to sector-specific technological changes: consumption and output. Technically speaking, consumption and output may Granger-cause future TFP for reasons which are orthogonal to ICT shocks. For example, the forward-looking nature of consumption may provide the VAR with information regarding future changes in TFP not related to an ICT shock, which our identification strategy is not able to filter out. Our second test is running a VAR in which we identify both ICT shocks and news shocks. In particular, we apply a sequential identification where we first identify a news shock in the spirit of \cite{barsky2011news}, and subsequently we identify our sectoral ICT shock using our original identification strategy. This second strategy has the specific purpose of filtering out all the current movements in forward-looking variables related to future fluctuations of TFP which are not related to current ICT shocks, as such fluctuations are all captured by the identified news shock.

As is illustrated in the rest of this section, both our robustness checks recover the same series for structural ICT shocks as our initial specification, and thus leave our results unaffected. We therefore conclude that controlling for signals regarding future movements in productivity does not affect our identified ICT shocks, and thus confirm the causal relation between current ICT investment and future TFP.
